DATA 621 - Business Analytics and Data Mining

### 2020-11-03 HW4/HW4_Draft.Rmd
Change stuff.

```{r corrgram, fig.width=6, fig.height=4}
corrplot(cor(DT[, ..nmtrnNUM], use = 'complete.obs'),
         method = 'ellipse', type = 'lower')
```

@@

 * `HOMEKIDS` with `KIDSDRIV`
   * This is self-explanatory
 * `HOME_VAL` with `INCOME`
   * Both are very strongly tied to wealth and net worth
 * `BLUEBOOK` and `INCOME`
   * People with more disposable income can afford more expensive vehicles
 * `CLM_FREQ` with `OLDCLAIM`
   * More claims implies a greater total aggregate payment
 * `CAR_AGE` and `INCOME`
   * This is interesting. It could be that people with higher disposable incomes
   buy more expensive cars and keep them for longer, but that's a guess.
 * `MVR_PTS` is *lightly* correlated with `CLM_FREQ` and `OLDCLAIM`
   * Probably when one is in a lot of accidents, the chances of them being at
   some level of fault rises
 * `HOMEKIDS` **negatively** correlated with `AGE`
   * As people age, their children age as well and eventually move out, we hope!

@@

 * `OWN` with `HOME_VAL` as discussed in the missing data section
 * `KIDSDRIV` with `HOMEKIDS`
 * A three-way interaction between `HOME_VAL`, `INCOME`, and `BLUEBOOK`
 * `CLM_FREQ` with `OLDCLAIM`
 * `MSTATUS` with `SEX`
   * One sex may be more affected by marriage than the other
 * `CAR_USE` with `URBANICITY`

```{r model1DummyFreq}
# Cast target as factor for caret purposes
trnFreq <- factor(trnX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
# Set up dummy variables
trnDumFreq <- dummyVars(TARGET_FLAG ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_AMT,
                        fullRank = TRUE, data = trnX)
# Create matrix of dummy values
trnXFD <- predict(trnDumFreq, newdata = trnX)
```

@@

```{r model1RunFreq, cache=TRUE}
# preProcess with near-zero value and kNN imputation
trnXFDpp <- preProcess(trnXFD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)

# Create processed predictors
trnXFDI <- predict(trnXFDpp, newdata = trnXFD)
trC <- trainControl(method = 'none',            # Using StepAIC
                    classProbs = TRUE,          # Classification
                    summaryFunction = prSummary # Precision/Recall
)
set.seed(487)
# Train Model
m1FreqFit <- train(x = trnXFDI, y = trnFreq, trControl = trC,
                   method = 'glmStepAIC', family = binomial(link = 'logit'),
                   direction = 'both', trace = 0)
# Print results
kable(summary(m1FreqFit$finalModel)$coefficients, digits = 3L,
      caption = "Model 1 Frequency Regression Output")
```

@@

Most of the coefficients are of the expected direction. For example, having
one's license revoked, living in an urban area, or increased travel times are
all *positive* risk factors while higher levels of wealth or education are
*negative* risk factors.

Some interesting observations. The predictors with the greatest effect on risk
are `URBANICITY` and `INCOME`. The value of the coefficient for `SEX` implies
that being female decreases the probability of a claim, as suspected, but it is
only significant as a predictor at the 10% level. However, it is kept in the
model as removing it increases the AIC. The hypothesized interaction between
`MSTATUS` and `SEX` does lower the deviance, but not enough to justify the
additional parameter. `BLUEBOOK` value is a negative risk factor. Perhaps people
with more expensive cars drive more carefully?

The full three-way interaction between `HOME_VAL`, `INCOME`, and `BLUEBOOK` was
deemed insignificant in light of the existing two-way interactions which are in
the model.

The interaction between `CLM_FREQ` and `OLDCLAIM` did help the model AIC, and
the coefficient indicates that while `OLDCLAIM` did not justify the additional
parameter, its tempering of `CLM_FREQ` **does** justify the additional
parameter.

@@

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. The further down the table the variable is,
the more dramatic its inclusion or exclusion will be on the deviance and theAIC.
The top 10 variables in order would be: `URBANICITY.Urban`,
`CAR_USECommercial:URBANICITYUrban`, `REVOKED.Yes`, `TRAVTIME`,
`CAR_TYPE.Sports Car`, `CLM_FREQ`, `TIF`, `MVR_PTS`, `CAR_TYPE.SUV`,
and `JOB.Blue Collar`.

```
                                      Df Deviance    AIC
<none>                                     5152.3 5212.3
+ HOMEKIDS                             1   5150.5 5212.5
+ AGE                                  1   5150.8 5212.8
+ EDUCATION.Masters                    1   5151.0 5213.0
- SEX.F                                1   5155.2 5213.2
+ JOB.Manager                          1   5151.6 5213.6
+ OLDCLAIM                             1   5151.6 5213.6
+ EDUCATION.PhD                        1   5151.7 5213.7
+ `HOME_VAL:BLUEBOOK`                  1   5151.7 5213.7
+ CAR_AGE                              1   5151.8 5213.8
- `INCOME:BLUEBOOK`                    1   5155.9 5213.9
+ OWN.Yes                              1   5152.1 5214.1
+ `MSTATUSYes:SEXF`                    1   5152.2 5214.2
+ RED_CAR.yes                          1   5152.3 5214.3
+ `EDUCATION.High School`              1   5152.3 5214.3
+ YOJ                                  1   5152.3 5214.3
+ `INCOME:HOME_VAL:BLUEBOOK`           1   5152.3 5214.3
+ CAR_USE.Commercial                   1   5152.3 5214.3
- `INCOME:HOME_VAL`                    1   5158.7 5216.7
- JOB.Student                          1   5159.0 5217.0
- JOB.Lawyer                           1   5159.1 5217.1
- `CAR_TYPE.Panel Truck`               1   5160.0 5218.0
- MSTATUS.Yes                          1   5162.6 5220.6
- CAR_TYPE.Van                         1   5166.3 5224.3
- BLUEBOOK                             1   5166.6 5224.6
- `JOB.Home Maker`                     1   5166.7 5224.7
- `OLDCLAIM:CLM_FREQ`                  1   5167.4 5225.4
- EDUCATION.Bachelors                  1   5169.0 5227.0
- HOME_VAL                             1   5169.5 5227.5
- PARENT1.Yes                          1   5169.9 5227.9
- INCOME                               1   5170.3 5228.3
- CAR_TYPE.Pickup                      1   5170.6 5228.6
- JOB.Professional                     1   5174.0 5232.0
- JOB.Clerical                         1   5181.7 5239.7
- KIDSDRIV                             1   5186.1 5244.1
- `JOB.Blue Collar`                    1   5189.2 5247.2
- CAR_TYPE.SUV                         1   5189.8 5247.8
- MVR_PTS                              1   5191.2 5249.2
- TIF                                  1   5191.8 5249.8
- CLM_FREQ                             1   5193.0 5251.0
- `CAR_TYPE.Sports Car`                1   5195.8 5253.8
- TRAVTIME                             1   5198.9 5256.9
- REVOKED.Yes                          1   5220.1 5278.1
- `CAR_USECommercial:URBANICITYUrban`  1   5229.9 5287.9
- URBANICITY.Urban                     1   5422.8 5480.8
```

### Severity Model
In the insurance world, severity is not necessarily fit via linear models, but
is more often fit through comparison of the maximum likelihood fits of various
distributional families to the size of the claims, but the task here is to fit a
linear regression model to estimate future claim size.

#### Training
The observations in the training set which have claim amounts greater than 0
will be extracted and used to fit the linear regression. Similar to frequency,
the model will be selected via a forward and backward stepwise AIC algorithm
starting with the same predictors and interactions as in the frequency model.

```{r model1DummySev}
# Extract those observations with values > 0
trnSev <- trnX[TARGET_AMT > 0, TARGET_AMT]
# Set up dummy variables
trnDumSev <- dummyVars(TARGET_AMT ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_FLAG,
                        fullRank = TRUE, data = trnX[TARGET_AMT > 0])
# Create matrix of dummy values
trnXSD <- predict(trnDumSev, newdata = trnX[TARGET_AMT > 0])
# preProcess with near-zero value and kNN imputation
trnXSDpp <- preProcess(trnXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)

# Create processed predictors
trnXSDI <- predict(trnXSDpp, newdata = trnXSD)
```

```{r runModel1Sev}
trC <- trainControl(method = 'none')
set.seed(878)
m1SevFit <- train(x = trnXSDI, y = trnSev, trControl = trC,
                  method = 'glmStepAIC', family = gaussian, direction = 'both',
                  trace = 0)
kable(summary(m1SevFit)$coefficients, digits = 3L,
      caption = "Model 1 Severity Regression Output")
```

@@

The predictive variables with the greatest effect on claim size are `OLD_CLAIM`,
`HOME_VAL`, and `BLUEBOOK`. The first and third make the most sense. One who has
had larger claims in the past is likely to have larger claims in the future.
Also, the claim for damages is very strongly correlated with the value of the
vehicle. `HOME_VAL` is a bit strange. Perhaps it's serving as a proxy for
purchased coverage limit. Maybe people with more expensive homes, who buy larger
limits on their homeowners policies, also purchase larger limits on their
vehicular polices.

The interaction between `INCOME` and `HOME_VAL` serves to temper the effect of
`HOME_VAL`. Similarly for the interaction between `OLDCLAIM` and `CLM_FREQ`.

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. There are only eight variables in the model,
and in order of AIC contribution they are `BLUEBOOK`, `OLDCLAIM`, `HOME_VAL`,
`INCOME:HOME_VAL`, `CAR_USE.Commercial`, `OLDCLAIM:CLM_FREQ`, `MSTATUS.Yes`, and
` REVOKED.Yes`.

```
                                      Df   Deviance   AIC
<none>                                   9.5456e+10 31329
- REVOKED.Yes                          1 9.5604e+10 31329
+ JOB.Manager                          1 9.5357e+10 31329
- MSTATUS.Yes                          1 9.5620e+10 31330
+ CAR_AGE                              1 9.5370e+10 31330
+ `MSTATUSYes:SEXF`                    1 9.5382e+10 31330
- `OLDCLAIM:CLM_FREQ`                  1 9.5636e+10 31330
- CAR_USE.Commercial                   1 9.5639e+10 31330
+ SEX.F                                1 9.5389e+10 31330
+ JOB.Professional                     1 9.5391e+10 31330
+ CAR_TYPE.Pickup                      1 9.5400e+10 31330
+ MVR_PTS                              1 9.5402e+10 31330
+ CAR_TYPE.Van                         1 9.5403e+10 31330
+ HOMEKIDS                             1 9.5404e+10 31330
+ CLM_FREQ                             1 9.5420e+10 31330
+ `CAR_USECommercial:URBANICITYUrban`  1 9.5426e+10 31330
+ RED_CAR.yes                          1 9.5430e+10 31331
+ JOB.Student                          1 9.5432e+10 31331
- `INCOME:HOME_VAL`                    1 9.5686e+10 31331
+ EDUCATION.Masters                    1 9.5435e+10 31331
- HOME_VAL                             1 9.5695e+10 31331
+ PARENT1.Yes                          1 9.5442e+10 31331
+ JOB.Clerical                         1 9.5445e+10 31331
+ `CAR_TYPE.Panel Truck`               1 9.5446e+10 31331
- OLDCLAIM                             1 9.5700e+10 31331
+ `EDUCATION.High School`              1 9.5446e+10 31331
+ OWN.Yes                              1 9.5447e+10 31331
+ TRAVTIME                             1 9.5448e+10 31331
+ `INCOME:HOME_VAL:BLUEBOOK`           1 9.5450e+10 31331
+ `JOB.Home Maker`                     1 9.5450e+10 31331
+ URBANICITY.Urban                     1 9.5453e+10 31331
+ `INCOME:BLUEBOOK`                    1 9.5454e+10 31331
+ AGE                                  1 9.5454e+10 31331
+ `HOME_VAL:BLUEBOOK`                  1 9.5455e+10 31331
+ `JOB.Blue Collar`                    1 9.5455e+10 31331
+ `CAR_TYPE.Sports Car`                1 9.5455e+10 31331
+ KIDSDRIV                             1 9.5456e+10 31331
+ JOB.Lawyer                           1 9.5456e+10 31331
+ EDUCATION.Bachelors                  1 9.5456e+10 31331
+ YOJ                                  1 9.5456e+10 31331
+ CAR_TYPE.SUV                         1 9.5456e+10 31331
+ INCOME                               1 9.5456e+10 31331
+ `KIDSDRIV:HOMEKIDS`                  1 9.5456e+10 31331
+ TIF                                  1 9.5456e+10 31331
+ EDUCATION.PhD                        1 9.5456e+10 31331
- BLUEBOOK                             1 9.6115e+10 31337
```

@@

```{r validateM1F}
# Model 1 Frequency:: process validation data similar to training data
tstFreq <- factor(tstX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
tstDumFreq <- dummyVars(TARGET_FLAG ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_AMT,
                        fullRank = TRUE, data = tstX)
tstXFD <- predict(tstDumFreq, newdata = tstX)
tstXFDpp <- preProcess(tstXFD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXFDI <- predict(tstXFDpp, newdata = tstXFD)

@@

# Model 1 Frequency: Calculate accuracy statistics
m1FCM <- confusionMatrix(m1Fpred, tstFreq, mode = 'everything')
freqCompTable[1, 2] <- m1FACC <- sum(diag(m1FCM$table)) / sum(m1FCM$table)
freqCompTable[1, 3] <- m1FF1 <- m1FCM$byClass[7]
freqCompTable[1, 4] <- m1FAUC <- auc(response = tstFreq,
                                     predictor = m1FpredProb[, 1])
```

@@

```{r validateM1S}
# Model 1 Severity: process validation data similar to training data
tstSev <- tstX[TARGET_AMT > 0, TARGET_AMT]
nobstst <- length(tstSev)
np <- summary(m1SevFit$finalModel)$df[3]
tstDumSev <- dummyVars(TARGET_AMT ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_FLAG,
                        fullRank = TRUE, data = tstX[TARGET_AMT > 0])
tstXSD <- predict(tstDumSev, newdata = tstX[TARGET_AMT > 0])
tstXSDpp <- preProcess(tstXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXSDI <- predict(tstXSDpp, newdata = tstXSD)

# Model 1 Severity: predict on validation data
m1Spred <- predict(m1SevFit, newdata = tstXSDI)

# Model 1 Severity: Calculate accuracy statistics
m1Ssum <- postResample(m1Spred, tstSev)
sevCompTable[1, 2] <- m1SRMSE <- m1Ssum[1]
sevCompTable[1, 3] <- m1SMAE <- m1Ssum[3]
m1SAR2 <- 1 - (1 - m1Ssum[2]) * (nobstst - 1) / (nobstst - np - 1)
sevCompTable[1, 4] <- m1SAR2
```

>>>>

```{r corrgram, fig.width=6, fig.height=4}
corrplot(cor(DT[, ..nmtrnNUM], use = 'complete.obs'),
         method = 'ellipse', type = 'lower', order = 'hclust',
         hclust.method = 'ward.D2')
```

@@

 * `HOMEKIDS` with `KIDSDRIV`
   * This is self-explanatory
 * `HOME_VAL` with `INCOME`
   * Both are very strongly tied to wealth and net worth
 * `BLUEBOOK` with`INCOME`
   * People with more disposable income can afford more expensive vehicles
 * `CLM_FREQ` with `OLDCLAIM`
   * More claims implies a greater total aggregate payment
 * `CAR_AGE` with `INCOME`
   * This is interesting. It could be that people with higher disposable incomes
   buy more expensive cars and keep them for longer, but that's a guess.
 * `MVR_PTS` is *lightly* correlated with `CLM_FREQ` and `OLDCLAIM`
   * Probably when one is in a lot of accidents, the chances of them being at
   some level of fault rises
 * `HOMEKIDS` **negatively** correlated with `AGE`
   * As people age, their children age as well and eventually move out, we hope!

@@

 * Three-way interaction between `OWN`, `HOME_VAL` and `INCOME`
   * Represents wealth
 * Three-way interaction between `CLM_FREQ`, `OLDCLAIM`, and `MVR_PTS`
   * Represents prior history
 * `CAR_USE` with `URBANICITY`
   * Represents increased risk of location

```{r model1DummyFreq}
# Cast target as factor for caret purposes
trnFreq <- factor(trnX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
# Set up dummy variables
trnDumFreq <- dummyVars(TARGET_FLAG ~ . +
                          OWN * HOME_VAL * INCOME +
                          CLM_FREQ * OLDCLAIM * MVR_PTS +
                          CAR_USE * URBANICITY -
                         INDEX - TARGET_AMT,
                        fullRank = TRUE, data = trnX)
# Create matrix of dummy values
trnXFD <- predict(trnDumFreq, newdata = trnX)
```

@@

```{r model1RunFreq}
# preProcess with near-zero value and kNN imputation
trnXFDpp <- preProcess(trnXFD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
# Create processed predictors
trnXFDI <- predict(trnXFDpp, newdata = trnXFD)
trC <- trainControl(method = 'none',            # Using StepAIC
                    classProbs = TRUE,          # Classification
                    summaryFunction = prSummary # Precision/Recall
)
set.seed(487)
# Train Model
m1FreqFit <- train(x = trnXFDI, y = trnFreq, trControl = trC,
                   method = 'glmStepAIC', family = binomial(link = 'logit'),
                   direction = 'both', trace = 0)
# Print results
kable(summary(m1FreqFit$finalModel)$coefficients, digits = 3L,
      caption = "Model 1 Frequency Regression Output")
```

@@

Most of the coefficients are of the expected direction. For example, having
one's license revoked, living in an urban area, or increased travel times are
all *positive* risk factors while higher levels of wealth or being married are
*negative* risk factors.

Some interesting observations. The predictors with the greatest effect on risk
are `URBANICITY` and the increased factor when it is a commercial vehicle. The
value of the coefficient for `SEX` implies that being female decreases the
probability of a claim, as suspected, but it is only significant as a predictor
at the 10% level. However, it is kept in the model as removing it increases the
AIC. `BLUEBOOK`, `INCOME`, and Having a `HOME_VAL` greater than 0 (as indicated
by the `OWN` variable being Yes) are all negative indicators, which supports the
hypothesis that people with greater wealth have fewer accidents. Those values
are tempered by some of the wealth interactions.

Every level of the interactions between `CLM_FREQ`, `OLDCLAIM`, and `MVR_PTS`
are significant.  What this may be telling us is that a linear regression is
***not*** the proper model for this analysis, and the algorithm is struggling to
add non-linearity via the interactions.

@@

Lastly, red cars do not contribute to increased claims frequency in this model.

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. The further down the table the variable is,
the more dramatic its inclusion or exclusion will be on the deviance and the
AIC.

```
                                      Df Deviance    AIC
<none>                                     5131.6 5199.6
- `OLDCLAIM:CLM_FREQ:MVR_PTS`          1   5134.4 5200.4
+ EDUCATION.Masters                    1   5130.6 5200.6
+ HOMEKIDS                             1   5130.7 5200.7
+ CAR_AGE                              1   5130.8 5200.8
- AGE                                  1   5134.9 5200.9
+ JOB.Manager                          1   5131.0 5201.0
- SEX.F                                1   5135.0 5201.0
+ HOME_VAL                             1   5131.1 5201.1
+ `HOME_VAL:OWNYes`                    1   5131.1 5201.1
+ EDUCATION.PhD                        1   5131.3 5201.3
+ YOJ                                  1   5131.6 5201.6
+ OWN.Yes                              1   5131.6 5201.6
+ EDUCATION.HighSchool                 1   5131.6 5201.6
+ RED_CAR.yes                          1   5131.6 5201.6
+ CAR_USE.Commercial                   1   5131.6 5201.6
- OLDCLAIM                             1   5135.9 5201.9
- JOB.Lawyer                           1   5137.6 5203.6
- `OLDCLAIM:MVR_PTS`                   1   5138.4 5204.4
- CAR_TYPE.PanelTruck                  1   5138.7 5204.7
- `CLM_FREQ:MVR_PTS`                   1   5138.9 5204.9
- `OLDCLAIM:CLM_FREQ`                  1   5139.0 5205.0
- JOB.Student                          1   5140.2 5206.2
- BLUEBOOK                             1   5141.1 5207.1
- INCOME                               1   5143.0 5209.0
- JOB.HomeMaker                        1   5143.1 5209.1
- CAR_TYPE.Van                         1   5144.0 5210.0
- PARENT1.Yes                          1   5144.7 5210.7
- MSTATUS.Yes                          1   5145.2 5211.2
- EDUCATION.Bachelors                  1   5148.1 5214.1
- `INCOME:HOME_VAL`                    1   5148.6 5214.6
- CAR_TYPE.Pickup                      1   5149.8 5215.8
- JOB.Professional                     1   5152.2 5218.2
- JOB.Clerical                         1   5156.9 5222.9
- `INCOME:OWNYes`                      1   5156.9 5222.9
- KIDSDRIV                             1   5164.6 5230.6
- JOB.BlueCollar                       1   5166.6 5232.6
- CLM_FREQ                             1   5168.5 5234.5
- TIF                                  1   5169.5 5235.5
- CAR_TYPE.SUV                         1   5169.8 5235.8
- MVR_PTS                              1   5176.4 5242.4
- CAR_TYPE.SportsCar                   1   5176.9 5242.9
- TRAVTIME                             1   5179.5 5245.5
- REVOKED.Yes                          1   5196.8 5262.8
- `CAR_USECommercial:URBANICITYUrban`  1   5207.3 5273.3
- URBANICITY.Urban                     1   5388.1 5454.1
```

### Severity Model
In the insurance world, severity is not necessarily fit via linear regression.
Rather, it is more often fit through comparison of the maximum likelihood fits
of various distributional families to the size of the claims, but the task here
is to fit a linear regression model to estimate future claim size.

#### Training
The observations in the training set which have claim amounts greater than 0
will be extracted and used to fit the linear regression. Similar to frequency,
the model will be selected via a forward and backward stepwise AIC algorithm
starting with the all the predictors. Experimentation with interactions only had
worse effects, so no interaction will be considered.

```{r model1DummySev}
# Extract those observations with values > 0
trnSev <- trnX[TARGET_AMT > 0, TARGET_AMT]
# Set up dummy variables
trnDumSev <- dummyVars(TARGET_AMT ~ . - INDEX - TARGET_FLAG,
                        fullRank = TRUE, data = trnX[TARGET_AMT > 0])
# Create matrix of dummy values
trnXSD <- predict(trnDumSev, newdata = trnX[TARGET_AMT > 0])
# preProcess with near-zero value and kNN imputation
trnXSDpp <- preProcess(trnXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
# Create processed predictors
trnXSDI <- predict(trnXSDpp, newdata = trnXSD)
```
```{r runModel1Sev}
trC <- trainControl(method = 'none', summaryFunction = defaultSummary,
                    classProbs = FALSE)
set.seed(878)
m1SevFit <- train(x = trnXSDI, y = trnSev, trControl = trC,
                  method = 'glmStepAIC', family = gaussian, direction = 'both',
                  trace = 0)
kable(summary(m1SevFit)$coefficients, digits = 3L,
      caption = "Model 1 Severity Regression Output")
```

@@

Unlike the frequency model, many of the resulting predictors are not significant
at even the 10% level. What this may be telling us is that a linear regression is
***not*** the proper model for this analysis, and the algorithm is struggling to
add non-linearity via the interactions. In practice, at the very least a GLM
with a gamma link would be tried or, more sophisticated predictive models such
as tree-based ones would be investigated. Most likely, MLE would be used to
estimate severity and a hierarchial contingent stocahstic cash flow model would
be built such that given a claim, a loss would be generated from a much more
amenable distribution, such as a Pareto or a Burr.

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. The further down the list a variable
preceded by a `-` is, the more drastic of an effect its removal would have on
the model AIC.

```
                       Df   Deviance   AIC
<none>                    9.5799e+10 31328
- CAR_AGE               1 9.5927e+10 31328
- OWN.Yes               1 9.5938e+10 31329
+ JOB.Manager           1 9.5696e+10 31329
- SEX.F                 1 9.5953e+10 31329
- MSTATUS.Yes           1 9.5960e+10 31329
+ MVR_PTS               1 9.5712e+10 31329
+ CAR_USE.Commercial    1 9.5729e+10 31329
+ REVOKED.Yes           1 9.5735e+10 31329
+ CAR_TYPE.Pickup       1 9.5748e+10 31330
+ JOB.Professional      1 9.5754e+10 31330
+ CAR_TYPE.Van          1 9.5757e+10 31330
+ HOMEKIDS              1 9.5763e+10 31330
+ CAR_TYPE.PanelTruck   1 9.5769e+10 31330
+ JOB.Student           1 9.5778e+10 31330
+ CLM_FREQ              1 9.5779e+10 31330
+ CAR_TYPE.SUV          1 9.5784e+10 31330
+ EDUCATION.Bachelors   1 9.5787e+10 31330
+ CAR_TYPE.SportsCar    1 9.5787e+10 31330
+ TRAVTIME              1 9.5788e+10 31330
+ PARENT1.Yes           1 9.5788e+10 31330
+ EDUCATION.HighSchool  1 9.5789e+10 31330
+ JOB.BlueCollar        1 9.5789e+10 31330
+ JOB.HomeMaker         1 9.5790e+10 31330
+ INCOME                1 9.5793e+10 31330
+ JOB.Lawyer            1 9.5793e+10 31330
+ OLDCLAIM              1 9.5794e+10 31330
+ TIF                   1 9.5795e+10 31330
+ KIDSDRIV              1 9.5796e+10 31330
+ YOJ                   1 9.5796e+10 31330
+ EDUCATION.PhD         1 9.5796e+10 31330
+ EDUCATION.Masters     1 9.5797e+10 31330
+ JOB.Clerical          1 9.5797e+10 31330
+ AGE                   1 9.5797e+10 31330
+ HOME_VAL              1 9.5797e+10 31330
+ URBANICITY.Urban      1 9.5798e+10 31330
+ RED_CAR.yes           1 9.5798e+10 31330
- BLUEBOOK              1 9.6748e+10 31341
```

@@

```{r validateM1F}
# Model 1 Frequency:: process validation data similar to training data
tstFreq <- factor(tstX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
tstDumFreq <- dummyVars(TARGET_FLAG ~ . +
                          OWN * HOME_VAL * INCOME +
                          CLM_FREQ * OLDCLAIM * MVR_PTS +
                          CAR_USE * URBANICITY -
                         INDEX - TARGET_AMT,
                        fullRank = TRUE, data = tstX)
tstXFD <- predict(tstDumFreq, newdata = tstX)
tstXFDpp <- preProcess(tstXFD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXFDI <- predict(tstXFDpp, newdata = tstXFD)

@@

# Model 1 Frequency: Calculate accuracy statistics
m1FCM <- confusionMatrix(m1Fpred, tstFreq, mode = 'everything')
freqCompTable[1, 2] <- m1FACC <- sum(diag(m1FCM$table)) / sum(m1FCM$table)
freqCompTable[1, 3] <- m1FF1 <- m1FCM$byClass[7]
freqCompTable[1, 4] <- m1FAUC <- auc(response = tstFreq,
                                     predictor = m1FpredProb[, 1])
m1FCM$table
```

@@

```{r validateM1S}
# Model 1 Severity: process validation data similar to training data
tstSev <- tstX[TARGET_AMT > 0, TARGET_AMT]
nobstst <- length(tstSev)
np <- summary(m1SevFit$finalModel)$df[3]
tstDumSev <- dummyVars(TARGET_AMT ~ . - INDEX - TARGET_FLAG,
                       data = tstX[TARGET_AMT > 0])
tstXSD <- predict(tstDumSev, newdata = tstX[TARGET_AMT > 0])
tstXSDpp <- preProcess(tstXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXSDI <- predict(tstXSDpp, newdata = tstXSD)

# Model 1 Severity: predict on validation data
m1Spred <- predict(m1SevFit, newdata = tstXSDI)
# Model 1 Severity: Calculate accuracy statistics
m1Ssum <- postResample(m1Spred, tstSev)
sevCompTable[1, 2] <- m1SRMSE <- m1Ssum[1]
sevCompTable[1, 3] <- m1SMAE <- m1Ssum[3]
m1SAR2 <- 1 - (1 - m1Ssum[2]) * (nobstst - 1) / (nobstst - np - 1)
sevCompTable[1, 4] <- m1SAR2
```
